---
title: "Jones Project"
author: Gwyneth Jones
output: html_notebook
---

Guiding Question: What factors directly impact risk of obesity?

```{r}
library(dcData)
library(ggplot2)
library(esquisse)
data("CountryData")
data("ProjectData")
```

Source Information:

-   Found on UC Irvine Machine Learning Repository and contained in the dcData package.

-   Collected by Fabio Mendoza Palechor, Alexis De la Hoz Manotas, and Matt Beckman

-   Collected as research for a paper in 2019 and as an accompanying resource for *Data Computing (2nd Edition)* by Kaplan & Beckman.

-   A case represents an individual, and there are 2111 cases. For CountryData, a case is a country and there are 256 cases.

-   I plan to analyze Gender, Age, Family History, Smoking, Water Consumption, Physical Activity, and Alcohol Consumption from ProjectData. From CountryData, I plan to use Population, Life, Health, Obesity, and Underweight as key variables.

```{r}
ggplot(ProjectData) +
  aes(x = family_history_with_overweight, fill = NObeyesdad) +
  geom_bar() +
  scale_fill_brewer(palette = "Dark2", direction = 1) +
  theme_bw() +
  facet_wrap(vars(Gender))
```


