---
title: "Jones Project"
author: Gwyneth Jones
output: html_notebook
---

Guiding Question: What lifestyle factors impact obesity?

```{r}
library(dcData)
library(ggplot2)
library(esquisse)
data("CountryData")
data("ProjectData")
```

Source Information:

-   Found on UC Irvine Machine Learning Repository and contained in the dcData package.

-   Collected by Fabio Mendoza Palechor, Alexis De la Hoz Manotas, and Matt Beckman

-   Collected as research for a paper in 2019 and as an accompanying resource for *Data Computing (2nd Edition)* by Kaplan & Beckman.

-   A case represents an individual, and there are 2111 cases. For CountryData, a case is a country and there are 256 cases.

-   I plan to analyze Gender, Age, Family History, Smoking, Water Consumption, Physical Activity, and Alcohol Consumption from ProjectData. From CountryData, I plan to use Population, Life, Health, Obesity, and Underweight as key variables.

```{r}
ggplot(ProjectData) +
  aes(x = family_history_with_overweight, fill = NObeyesdad) +
  geom_bar() +
  scale_fill_brewer(palette = "Dark2", direction = 1) +
  theme_bw() +
  facet_wrap(vars(Gender))
```

```{r}
CountryNew %>%
  select(country, life, health, obesity, underweight)
```

Preliminary Observations:

A family history of obesity seems to impact the development of obesity in both males and females. Overweight type I and II appear about equally for men and women with a family history of obesity, while obesity type I and II are more common for men, and obesity type I and III are more common for women.Without a family history of obesity, women tend to be more underweight or overweight type I, while men tend to be more normal weight or overweight type I. Mexico allots the most funding towards healthcare, but also has 32.1% of the population considered obese. Peru has the least funding towards healthcare, and has the lowest obesity rate. However, Peru does have a lower lifespan than Colombia and Mexico, and has the highest incidence of underweight individuals in the population.

Intuition:

I have a feeling that the most common relation to obesity development is a family history for both males and females, and I'm curious to see how other variables might be at play.
